SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-14 docs/questioning.tex
pass in III

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks associated
with source code injection. Figure~\ref{fig:attacks}
presents the steps of different application attacks. Links between
steps are labeled with the paths constituting different attacks. The
sequence of steps for each attack is shown by the numbers next to the
attack names in the labels. Most steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Large crosses on transitions in
Figure~\ref{fig:attacks} indicate the points where defenses detect
attacks.

A malicious user can initiate the attack through two different routes.
The attacker may use the browser of an innocent user as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc
  url} and then trick an end user to click on it via social
engineering (i.e., phishing, through transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code in the application (through
transition {\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
in a web application that accepts and redisplays user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users or embed malicious
{\sc sql} code to retrieve all the password entries from a database.
Recall the examples we provided in Section~\ref{sec:attacks}.
Note that an {\sc xss} attack can start from both routes.

@@

{\sc xss} attacks fall into two categories, {\it non-persistent} and
{\it persistent}. Non-persistent {\sc xss} attacks take place when the
data provided by a user is used immediately by server-side scripts to
parse and display a page of results, without properly sanitizing the
request (transition {\sc p-xss} 7, {\sc n-xss} 2).
Thus, in a non-persistent {\sc xss} attack the injected code
is never saved on the server and immediately becomes part of the
content that is sent back to a web user.

In persistent {\sc xss} attacks malicious code is saved by the server.
The injected code that is stored on the server-side re-enters the
application's execution flow and becomes part of the content that is
actually sent back afterwards to the user.

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps-new.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on source code injection.
For every arrow there are corresponding transition numbers for
every attack. Every {\it point} indicates a transition where mechanisms
detect attacks. For every point we provide the corresponding
references:
Point {\sc ub} (at the user's browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
Point {\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
Point {\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
Point i{\sc db} (in the database):~\cite{BK04,LLW02,VMV05}.}
\end{figure*}

>>>>

In this section we provide a step-by-step exploitation model to
understand the process of carrying out source code injection attacks
against web applications.
Figure~\ref{fig:attacks}
presents the required steps for different classes of injection attacks.
Links between steps are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Most steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Large `X' marks on transitions 
indicate the points where defenses detect or prevent attacks.

An attacker can initiate an injection attack through two different main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an HTTP request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1)
or embed malicious
{\sc sql} code to retrieve the password entries from a database ({\sc dsl} 1).
%Recall the examples we provided in Section~\ref{sec:attacks}.
Note that {\sc xss} attacks can start from both routes.

@@

{\sc xss} attacks fall into two categories, {\it non-persistent} and
{\it persistent}. Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and end up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server and immediately becomes part of the
content that is sent back to a web user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
actually sent back to the user as part of a future response.

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps-new.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model for dynamic and domain specific
language code injection in web applications.
Transitions are labeled with the different attacks that use that path,
while the numbers next to attack labels denote the 
sequence of steps for a particular attack.
Points where different types of defenses
detect or prevent attacks are marked with an `X' symbol:
{\sc ub} (browser):~\cite{KJKV09,LV09,TNH07,NSS06,APKLM10,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,VFJKKV07,SLMS14,BV08},
{\sc s}t{\sc b} (en route from the server to the browser):~\cite{RDWDE07,JKK06a,GC09,JB07,NLC07,WPLKK09,JEP08,PS11},
{\sc e}i{\sc q} (embedded in a query en route to the database):~\cite{BWS05,SW06,HCF05,XBS06,PB05,PMP11,MS09,HO05,SMS13},
Point i{\sc db} (at the database):~\cite{BK04,LLW02,VMV05}.}
\end{figure*}
